TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-07-19 paper/draft.tex
take out some figs

The three panels of \ref{fig:safe_selection} show before and after selection of the sources in \gaia\ color-magnitude space, colored by \thecannon\ determined temperatures, metallicities, and spectral types, with their respective training samples overplotted in orange. Each plot shows the expected gradient: temperature increases with decreasing color, spectral subtype increases with increasing color, and metallicity gradient increases perpendicularly to the main sequence branch. Additionally we notice a slight deviation at the upper slice of the main sequence where \cannon\ temperatures, metallicities and spectral types all appear lower than the gradient trends in the rest of the branch, which is most likely the binary sequence. Comparisons between the West-trained spectral types and Mann-trained temperatures and metallicities are shown in Figure \ref{fig:west_vs_mann}: left shows the slight negative correlation between spectral type and $\feh$, and right shows the nonlinear decrease in temperature with visible metallicity gradient. We also note that applying our model requires very little computational demand: the time to train and test a model on all 14,827 sources was two minutes on a personal laptop.

@@

% \begin{figure*}[hp!]
% 	\includegraphics[width=\linewidth]{figures/isochrone_cmd.png}
% 	\caption{Comparison of \cannon\ $\feh$ as compared to metallicity predicted by PARSEC isochrone tracks \citealt{Bressan:2012} in \gaia\ color-magnitude space. The four panels show five metallicity tracks (ranging $-0.5<$[M/H]$<0.5$) over varying ages (1, 3, 5, and 7 Gyr).}
% 	\label{fig:isochrone_cmd}
% \end{figure*}

\begin{figure}
	\includegraphics[width=\linewidth]{figures/cannon_vs_parsec.png}
	\includegraphics[width=\linewidth]{figures/aspcap_vs_parsec1.png}
	\caption{Comparison of \cannon\ $\feh$ as compared to metallicity predicted by PARSEC isochrone tracks \citep{Bressan:2012} in \gaia\ color-magnitude space. The two panels show five metallicity tracks (ranging $-0.5<$[M/H]$<+0.5$ in steps of 0.1 dex) at two different ages (3 and 7 Gyr). In the ASPCAP plot only the 8,960 out of 10,311 sources with metallcities $-0.5<$[M/H]$<+0.5$ are shown, while the remaining 1,351 sources with [M/H]$<-0.5$ and [M/H]$>+0.5$.}
	\label{fig:isochrone_cmd}
\end{figure}

% \begin{figure}
% 	\includegraphics[width=\linewidth]{figures/aspcap_vs_parsec2.png}
% 	\caption{}
% 	\label{fig:isochrone_cmd_2}
% \end{figure}

\begin{figure*}
	\plotone{figures/aspcap_cannon_label_hist.png}
	\caption{Distribution of temperatures and metallicities for 10,311 sources from \thecannon\ compared to the ASPCAP pipeline. Note that \cannon\ temperatures only span $2850<T_{\rm eff}<4150$ and $-0.5<\feh<0.5$\,dex because we have imposed cutoffs for stars that fall outside of the training sample range, however for the same 10,311 stars ASPCAP predictions are skewed higher in temperature and lower in metallicity compared to \cannon\ measurements.}
	\label{fig:aspcap_cannon_label_hist} 
\end{figure*}

Figure \ref{fig:isochrone_cmd} \\

% JB DO WE WANT A FIGURE THAT SHOWS ABUNDANCES AS A FUNCTION OF MILKY WAY POSITION OR ACTIONS?

@@

\begin{figure*}[h]
	\plotone{figures/spt_vs_teff_vs_feh.png}
	\caption{West-trained spectral types vs. Mann-trained metallcities and temperatures. For each integer spectral type bin the mean temperatures and metallicities are shown as red error boxes. \label{fig:west_vs_mann}}
\end{figure*}

@@

% \newpage

@@

>>>>

The three panels of \ref{fig:safe_selection} show before and after selection of the sources in \gaia\ color-magnitude space, colored by \thecannon\ determined temperatures, metallicities, and spectral types, with their respective training samples overplotted in orange. Each plot shows the expected gradient: temperature increases with decreasing color, spectral subtype increases with increasing color, and metallicity gradient increases perpendicularly to the main sequence branch. Additionally we notice a slight deviation at the upper slice of the main sequence where \cannon\ temperatures, metallicities and spectral types all appear lower than the gradient trends in the rest of the branch, which is most likely the binary sequence. 
% Comparisons between the West-trained spectral types and Mann-trained temperatures and metallicities are shown in Figure \ref{fig:west_vs_mann}: left shows the slight negative correlation between spectral type and $\feh$, and right shows the nonlinear decrease in temperature with visible metallicity gradient. 
We also note that applying our model requires very little computational demand: the time to train and test a model on all 14,827 sources was two minutes on a personal laptop.

@@

% \begin{figure}
% 	\includegraphics[width=\linewidth]{figures/cannon_vs_parsec.png}
% 	\includegraphics[width=\linewidth]{figures/aspcap_vs_parsec1.png}
% 	\caption{Comparison of \cannon\ $\feh$ as compared to metallicity predicted by PARSEC isochrone tracks \citep{Bressan:2012} in \gaia\ color-magnitude space. The two panels show five metallicity tracks (ranging $-0.5<$[M/H]$<+0.5$ in steps of 0.1 dex) at two different ages (3 and 7 Gyr). In the ASPCAP plot only the 8,960 out of 10,311 sources with metallcities $-0.5<$[M/H]$<+0.5$ are shown, while the remaining 1,351 sources with [M/H]$<-0.5$ and [M/H]$>+0.5$.}
% 	\label{fig:isochrone_cmd}
% \end{figure}

% \begin{figure*}
% 	\plotone{figures/aspcap_cannon_label_hist.png}
% 	\caption{Distribution of temperatures and metallicities for 10,311 sources from \thecannon\ compared to the ASPCAP pipeline. Note that \cannon\ temperatures only span $2850<T_{\rm eff}<4150$ and $-0.5<\feh<0.5$\,dex because we have imposed cutoffs for stars that fall outside of the training sample range, however for the same 10,311 stars ASPCAP predictions are skewed higher in temperature and lower in metallicity compared to \cannon\ measurements.}
% 	\label{fig:aspcap_cannon_label_hist} 
% \end{figure*}

@@

% \begin{figure*}[h]
% 	\plotone{figures/spt_vs_teff_vs_feh.png}
% 	\caption{West-trained spectral types vs. Mann-trained metallcities and temperatures. For each integer spectral type bin the mean temperatures and metallicities are shown as red error boxes. \label{fig:west_vs_mann}}
% \end{figure*}

@@

\newpage

@@

\newpage
